Viral Sequence Sorting Tools - Rules on Fragments

### 2023-04-15 TestingPipeline/Scripts/paper_figure_generation.Rmd
TV vs TNV rule analysis.

@@

>>>>

## visualizing a select set of tools
```{r}
viruses$keep_score_high_tv_tnv <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = F,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = F)
viruses$keep_score_high_tv <- getting_viral_set_1(viruses, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = F,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = F,
                                              include_virsorter = F)

viruses$tv_vs_tv_ntv <- "not tv"
viruses$tv_vs_tv_ntv[viruses$keep_score_high_tv>=1 & viruses$keep_score_high_tv_tnv>=1] <- "tnv_preserved"
viruses$tv_vs_tv_ntv[viruses$keep_score_high_tv>=1 & viruses$keep_score_high_tv_tnv<1] <- "tnv lost"

table(viruses$tv_vs_tv_ntv, viruses$true_virus)

@@

# Comparing RefSeq vs VS2 database
VS2 sequences used: (/scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/NCLDV/env/NCLDV_env.fna /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/lavidaviridae/env/HQ_virophages.fna /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/dsDNAphage/env/* /scratch/kwigg_root/kwigg/hegartyb/VSTE/non-refseq-genomes/dsDNAphage/provirus/VirSorterCuratedDataset_HQ_contigs.fna)

```{r}
refseq_vir <- read_tsv("../IntermediaryFiles/refseq_viral_genome_ids.txt",col_names = F)
refseq_vir$X1 <- sub(">", "", refseq_vir$X1)
refseq_vir <- separate(refseq_vir, col=X1, sep=" ", remove=T, into="id")
refseq_vir$id <- sub("\\.", "_", refseq_vir$id)
```

```{r}
table(refseq_vir$id %in% viruses$contig)
```

```{r}
viruses_refseq_vir <- viruses[viruses$contig %in% refseq_vir$id,]
viruses_not_refseq_vir <- viruses[!(viruses$contig %in% refseq_vir$id) & viruses$seqtype=="virus",]
```

```{r}
table(viruses_refseq_vir$max_score_group)
table(viruses_not_refseq_vir$max_score_group)
```

```{r}
viruses_refseq_vir$keep_score_high_MCC <- getting_viral_set_1(viruses_refseq_vir, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = T,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = F)

viruses_not_refseq_vir$keep_score_high_MCC <- getting_viral_set_1(viruses_not_refseq_vir, include_deepvirfinder = F,
                                              include_vibrant = F,
                                              include_virsorter2 = T,
                                              include_tuning_viral = T,
                                              include_tuning_not_viral = T,
                                              include_virsorter = F)
```

```{r}
sum(viruses_refseq_vir$keep_score_high_MCC>=1)/nrow(viruses_refseq_vir)
```

```{r}
sum(viruses_not_refseq_vir$keep_score_high_MCC>=1)/nrow(viruses_not_refseq_vir)
```

### 2023-04-15 TestingPipeline/Scripts/visualizing_rules_on_short_fragments.Rmd
TV vs TNV rule analysis.

Import the file that combines the results from each of the tools from running "combining_tool_output-fragments.Rmd":
```{r}
viruses <- read_tsv("../IntermediaryFiles/viral_tools_combined-fragments.tsv")
```

>>>>

Import the file that combines the results from each of the tools from running "combining_tool_output-fragments.Rmd":
```{r}
viruses <- read_tsv("../IntermediaryFiles/viral_tools_combined-fragments.tsv")
```
```{r}
viruses$kaiju_match_ratio_color <- "less than 0.3"
viruses$kaiju_match_ratio[viruses$kaiju_match_ratio>=0.3] <- "greater than or equal to 0.3"

ggplot(viruses, aes(x=kaiju_match_ratio, color=kaiju_match_ratio_color, fill=kaiju_match_ratio_color)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(~seqtype, scales = "free") +
  #scale_color_viridis_d(begin=0.2, end=0.8) +
  #scale_fill_viridis_d(begin=0.2, end=0.8, alpha=0.2) +
  xlab("Kaiju Match Ratio")
```
